\section{Glossary}
\label{sec:glossary}

\emph{Program}: The general term for the application being developed.

\emph{Client}: The general term of the client side of the program

\emph{WebClient}: The browser based client of the program. Lets users access the server through a browser

\emph{Desktop Client}: The desktop client of the program. Lets users access the server through the desktop

\emph{System}: The current system being used. This can be either the desktop client or the web client based on the context

\emph{Server}: The server containing the database. The server is being contacted by the clients to retrieve the requested information.

\emph{Movie}: An entity in the database containing information about a specific movie. A movie can be a specific episode of a series

\emph{Series}: A collection of movies (episodes).

\emph{Person}: An entity in the database containing information about a specific person. Persons can be actors or directors.

\emph{User}: An entity in the database containing information about a specific user. Users are accounts made to personalize the experience of the program

\emph{Adminstrator}: A user with permission to edit data in the database through the clients.

\emph{Favourites List}: A list of movies that a user wants to have easy access to later. Each user has one favourite list.

\emph{MyMovieAPI}: A way of getting movies directly from the actual IMDB server. This is utilized whenever the contents of our own server is insufficient. http://mymovieapi.com/
