\chapter{Requirements Analysis Document}

\section{Introduction}
\label{sec:introduction}

\subsection{Revision History}
\begin{center}
    \begin{tabular}{ | l | l | p{6cm} | p{4cm} |}
    \hline
    Version & Date & Description & Author(s) \\ \hline
    0.1.0 & 19/11/2013 & Initial Document & MIFR, JKAS, MJUP, JBEC, MKIN, MORR
    \\ \hline
    0.2.0 & 20/11/2013 & Added scenarios and use cases & MIFR, JKAS, MJUP, JBEC, MKIN
    \\ \hline
    0.3.0 & 20/11/2013 & Added glossary, functional and non-functional requirements, object model, Use case diagram, State machine diagram and refined introduction formulation & MIFR, JKAS, MJUP, JBEC, MKIN
    \\ \hline
    0.4.0 & 21/11/2013 & Refined scenarios, added sequence diagrams, added boundary objects & MIFR, JKAS, MJUP, JBEC, MKIN, MORR
    \\ \hline
    1.0.0 & 10/12/2013 & Complete revision of the RAD. Reworked functional and non-functional requirements to fit what we are actually able to do & MIFR
    \\ \hline
    1.1.0 & 11/12/2013 & Removed irrelevant scenarios and use cases, spell checked & MIFR, MORR
    \\ \hline
    1.2.0 & 12/12/2013 & Revised glossary, added updated sequence diagrams and use case diagrams & MIFR, MORR
    \\ \hline
    1.2.1 & 13/12/2013 & Revised a non-functional requirement slightly & MIFR
    \\ \hline
    \end{tabular}
\end{center}

\subsection{Purpose of the system}

The purpose of the system is to create a tool for people watching movies. We want to give our users access to a movie database available at their fingertips for inspiration and the possibility to read about their favourite movies.

Two clients shall be available . A browser based client enabling access from a browser, as well as a desktop application for their personal computer.  


%Init formulation The purpose of the system is to create a tool for easy access to a movie database through the use of two clients: A desktop- and browser-version.


\subsection{Scope of the system}

The scope of the system is as follows

Scope is making a system containing most movies with related information, and making this data available though a distributed RESTful web service. Two clients will also be implemented: An ASP.net web browser client, and a desktop application done with WPF.

Part of the scope will also be to work with responsiveness enabling caching and database optimizing through indexing and optimized SQL quires.

Out of scope is looking into user security issues

%Init definition
%\begin{itemize}
%\item A Database which contains most movies related information
%\item An Application Server which exposes services making the Database %information accessible
%\item A Desktop Client which presents the user with movie information from the %Database
%\item A Web Client which also presents the user with movie information from the %Database
%\end{itemize} 

\subsection{Objectives and success criteria of the project}

The success criteria for this project is reached if end-users, in an easy and fast manner, are able to find movie information through both the desktop- and web-client. Success will be measured by how many users, without complications, are able to use our system to find desired information.

This goal is achieved if 9/10 users are able to do so.

%Init definition
%The success criteria for this project is reached if end-users, in an easy and fast manner, are able to find movie information through both the desktop- and web-client.

